\tcode{Generalisation of nth_element to a range of nths}

### 2021-12-07 draft_lundberg_nth_elements.tex
spell fix, link and example of image / histogram equalization

\begin{tabular}{ll}
Document \#:& P2375R0 \\
Date: &2021-05-14 \\
Project: & Programming Language C++ \\
Audience: & LEWG \\
Email: &\href{mailto:lundberj@gmail.com}{lundberj@gmail.com}
\end{tabular}

@@

@@

\begin{codeblock}
stuct Pony{
  double littleness; 
  chrono::duration age;
  string name;
};
auto end=nth_elements(v, nths, std::greater{}, Pony::age);
std::sort(nths[3], nths[4], std::less{}, Pony::name);
\end{codeblock}

>>>>

\begin{tabular}{ll}
Document \#:& P2375 D1 \\
Date: &2021-05-14 \\
Project: & Programming Language C++ \\
Audience: & LEWG \\
Email: &\href{mailto:lundberj@gmail.com}{lundberj@gmail.com}
\end{tabular}

@@

\subsection*{Revision history vs R0}

Fixed typo. (23021-12-06)

@@

\begin{codeblock}
struct Pony{
  double littleness; 
  chrono::duration age;
  string name;
};
auto end=nth_elements(v, nths, std::greater{}, Pony::age);
std::sort(nths[3], nths[4], std::less{}, Pony::name);
\end{codeblock}
